Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2023-07-20 src/docs_paper/paper.Rmd
Custom version of the Naomi output figure #55

```{r naomi-results, fig.cap="District-level model outputs for adults aged 15-49. Inference conducted using TMB."}
knitr::include_graphics("depends/naomi-results.png")

# Eventually this figure should be generated using PCA-AGHQ
# knitr::include_graphics("depends/figB.png")
```

>>>>

```{r naomi-results, fig.cap="District-level HIV prevalence (A), ART coverage (B), and HIV incidence and new cases (C) for adults 15-49 in Malawi. Inference conducted using TMB."}
knitr::include_graphics("figB.png")
```
